### 2022-09-14 input/proposal.tex
Typos to cope with American english

In this paper, we consider Edge infrastructures as a set of
interconnected autonomous systems comprising heterogeneous \nodes
interconnected by communication links. \Processes involved in the
management of content may crash but are not byzantine.  \Processes can
reliably communicate through asynchronous message passing to other
known \processes called neighbors.  We define scoped broadcast as a
communication primitive that propagates a message around its
broadcaster within an application-dependant scope.

@@

At any time, a \process can decide to become a \emph{source}, hence
creating a new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring \processes that are closer to this source than any other
one. Such a distance (or \emph{weight}) is application-dependant: in
the context of maintaining distributed indexes, this would be about
link latency that \nodes could monitor by aggregating \texttt{ping}s;
or operational costs when dealing with multiple tenants.

>>>>

In this paper, we consider Edge infrastructures as a set of
interconnected autonomous systems comprising heterogeneous \nodes
interconnected by communication links. \Processes involved in the
management of content may crash but are not byzantine.  \Processes can
reliably communicate through asynchronous message passing to other
known \processes called neighbors.  We define scoped broadcast as a
communication primitive that propagates a message around its
broadcaster within an application-dependent scope.

@@

At any time, a \process can decide to become a \emph{source}, hence
creating a new partition in the system by executing an \texttt{Add}
operation. This partition includes at least its source plus
neighboring \processes that are closer to this source than any other
one. Such a distance (or \emph{weight}) is application-dependent: in
the context of maintaining distributed indexes, this would be about
link latency that \nodes could monitor by aggregating \texttt{ping}s;
or operational costs when dealing with multiple tenants.
